Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-06 Paper.tex
Execution model fixes.

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{f0s: System operations}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0xf0 & {\small CREATE} & 5 & 1 & Create a new contract. \\
&&&& $\mathbf{b} \equiv \mathbb{M}_M[ \mathbb{M}_S[1] \dots (\mathbb{M}_S[1] + \mathbb{M}_S[2] - 1) ]$ \\
&&&& $\mathbf{i} \equiv \mathbb{M}_M[ \mathbb{M}_S[3] \dots (\mathbb{M}_S[3] + \mathbb{M}_S[4] - 1) ]$ \\
&&&& $(\mathbb{S}', \mathbb{M}'_g) \equiv \Lambda(\mathbb{S}, I_a, I_o, \mathbb{M}_g, I_p, \mathbb{M}_S[0], \mathbf{i}, \mathbf{b})$ \\
\midrule
0xf1 & {\small CALL} & 7 & 1 & Message-call into contract. \\
&&&& $\mathbf{i} \equiv \mathbb{M}_M[ \mathbb{M}_S[3] \dots (\mathbb{M}_S[3] + \mathbb{M}_S[4] - 1) ]$ \\
&&&& $\mathbf{o} \equiv \mathbb{M}_M[ \mathbb{M}_S[5] \dots (\mathbb{M}_S[5] + \mathbb{M}_S[6] - 1) ]$ \\
&&&& Let $g_k = \begin{cases}0 & \text{if} \quad \mathbb{M}_S[2] = 0 \\ \mathbb{M}_g - \min(\mathbb{M}_g, \mathbb{M}_S[2]) & \text{otherwise} \end{cases}$ \\
&&&& $(\mathbb{S}', g', \mathbf{o}) \equiv \Theta(\mathbb{S}, I_a, I_o, \mathbb{M}_S[0], g, I_p, \mathbb{M}_g - g_k, \mathbb{M}_S[1], \mathbf{i})$ \\
&&&& $\mathbb{M}'_g \equiv g' + g_k$ \\
\midrule
0xf2 & {\small RETURN} & 2 & 0 & Halt execution returning output data. \\
&&&& $H_{\text{\tiny RETURN}}(\mathbb{M}) \equiv \mathbb{M}_M[ \mathbb{M}_T[0] \dots ( \mathbb{M}_T[0] + \mathbb{M}_T[1] - 1 ) ]$ \\
&&&& This has the effect of halting the execution at this point with output defined.\\
&&&& See section \ref{ch:model}. \\
\midrule
0xff & {\small SUICIDE} & 1 & 0 & Halt execution and obliterate account. \\
&&&& $\mathbb{S}'[\mathbb{M}_T[0]]_{balance} \equiv \mathbb{S}[\mathbb{M}_T[0]]_{balance} + \mathbb{S}[I_a]_{balance}$ \\
&&&& $\mathbb{S}'[I_a] \equiv \varnothing$ \\
\bottomrule
\end{tabular*}

>>>>

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{f0s: System operations}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0xf0 & {\small CREATE} & 5 & 1 & Create a new contract. \\
&&&& $\mathbf{b} \equiv \mathbb{M}_M[ \mathbb{M}_S[1] \dots (\mathbb{M}_S[1] + \mathbb{M}_S[2] - 1) ]$ \\
&&&& $\mathbf{i} \equiv \mathbb{M}_M[ \mathbb{M}_S[3] \dots (\mathbb{M}_S[3] + \mathbb{M}_S[4] - 1) ]$ \\
&&&& $(\mathbb{S}', \mathbb{M}'_g) \equiv \Lambda(\mathbb{S}, I_a, I_o, \mathbb{M}_g, I_p, \mathbb{M}_S[0], \mathbf{i}, \mathbf{b})$ \\
&&&& $\mathbb{M}'_T[0] \equiv x$ \\
&&&& where $x=0$ if the code execution for this operation failed due to lack of gas;\\
&&&& $x=A(I_a, \mathbb{S}[I_a]_{nonce})$, the address of the newly created contract, otherwise. \\
\midrule
0xf1 & {\small CALL} & 7 & 1 & Message-call into contract. \\
&&&& $\mathbf{i} \equiv \mathbb{M}_M[ \mathbb{M}_S[3] \dots (\mathbb{M}_S[3] + \mathbb{M}_S[4] - 1) ]$ \\
&&&& $\mathbf{o} \equiv \mathbb{M}_M[ \mathbb{M}_S[5] \dots (\mathbb{M}_S[5] + \mathbb{M}_S[6] - 1) ]$ \\
&&&& Let $g_k = \begin{cases}0 & \text{if} \quad \mathbb{M}_S[2] = 0 \\ \mathbb{M}_g - \min(\mathbb{M}_g, \mathbb{M}_S[2]) & \text{otherwise} \end{cases}$ \\
&&&& $(\mathbb{S}', g', \mathbf{o}) \equiv \Theta(\mathbb{S}, I_a, I_o, \mathbb{M}_S[0], g, I_p, \mathbb{M}_g - g_k, \mathbb{M}_S[1], \mathbf{i})$ \\
&&&& $\mathbb{M}'_g \equiv g' + g_k$ \\
&&&& $\mathbb{M}'_T[0] \equiv x$ \\
&&&& where $x=0$ if the code execution for this operation failed due to lack of gas;\\
&&&& $x=1$ otherwise. \\
\midrule
0xf2 & {\small RETURN} & 2 & 0 & Halt execution returning output data. \\
&&&& $H_{\text{\tiny RETURN}}(\mathbb{M}) \equiv \mathbb{M}_M[ \mathbb{M}_T[0] \dots ( \mathbb{M}_T[0] + \mathbb{M}_T[1] - 1 ) ]$ \\
&&&& This has the effect of halting the execution at this point with output defined.\\
&&&& See section \ref{ch:model}. \\
\midrule
0xff & {\small SUICIDE} & 1 & 0 & Halt execution and obliterate account. \\
&&&& $\mathbb{S}'[\mathbb{M}_T[0]]_{balance} \equiv \mathbb{S}[\mathbb{M}_T[0]]_{balance} + \mathbb{S}[I_a]_{balance}$ \\
&&&& $\mathbb{S}'[I_a] \equiv \varnothing$ \\
\bottomrule
\end{tabular*}
